Notes on area-length problem for CLE

### 2013-11-27 area-length/notes.tex
Minor changes

Partition function for $O(n)$ model is
\begin{equation}
  \label{eq:9}
  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
  n^{\mbox{number of loops}}
\end{equation}

@@

\section{Scaling limit and CFT on a cone}
\label{sec:scaling-limit-cft}

@@

>>>>

Partition function for $O(n)$ model is
\begin{equation}
  \label{eq:9}
  Z_{O(n)} = \sum_{\mbox{loop conf}} x^{\mbox{total length}}
  n^{\mbox{number of loops}}
\end{equation}
Critical point is $x=\frac{1}{\sqrt{2+\sqrt{2-n}}}$, the continuum
limit in this point is described by minimal model $(p,p')$ with
$n=-2\cos\left(\frac{\pi p}{p'}\right)$. $c=1-6\frac{(p-p')^2}{pp'}$, $b=$.

Self-avoiding walk is obtained in the limit $n\to 0$. Then $c=0$ and
we have logarithmic conformal field theory.

@@

\section{Liouville theory}
\label{sec:liouville-theory}

Liouville theory, flat metric, asymptotic for field, Coulomb gas formalism.

The action for Liouville theory on a surface $\Gamma$ in arbitrary world-sheet metric $g$ is
\begin{equation}
  \label{eq:13}
  S=\frac{1}{4\pi} \int_{\Gamma} \sqrt{g} \left( g^{ab} \partial_{a}\varphi \partial_{b}\varphi + Q R \varphi +4\pi \mu e^{2b\varphi}\right) d^{2}x
\end{equation}
Classical equations of motion are
\begin{equation}
  \label{eq:16}
  \Delta \varphi(x) = \frac{1}{2} \left(b+\frac{1}{b}\right) R (x) + 4\pi b e^{2 b \varphi}
\end{equation}
Here $\Delta$ is Laplace-Beltrami operator
\begin{equation}
  \label{eq:17}
  \Delta=\frac{1}{\sqrt{g}}\partial_{\mu} \left(\sqrt{g} g^{\mu\nu} \partial_{\nu}\right)
\end{equation}

We can select locally flat metric $g^{ab}=\delta^{ab}$ on some sheet, then the action takes the form
\begin{equation}
  \label{eq:14}
  S= \int d^{2}x \frac{1}{4\pi} (\partial_{a} \varphi)^{2}+\mu e^{2b\varphi}
\end{equation}
Since we rewrote the action in this form we need to take into account the curvature. We do it by
supposing the existence of conical singularity at infinity.
\begin{equation}
  \label{eq:15}
  \varphi(z)=-Q \log (z\bar z)+O(1) \quad z\to\infty
\end{equation}
The equations of motion take the from
\begin{equation}
  \label{eq:18}
  \Delta \varphi = 4\pi b e^{2b\varphi}
\end{equation}
The background charge is connected with the parameter $b$ by equation
\begin{equation}
  \label{eq:20}
  Q=b+\frac{1}{b}
\end{equation}

Liouville field theory is a conformal field theory with central charge
\begin{equation}
  \label{eq:19}
  c=1+6\left(b+\frac{1}{b}\right)^{2}
\end{equation}
and primary fields are given by vertex operators $V_{\alpha}=e^{\alpha\varphi}$. But primary fields
$V_{\alpha}$ and $V_{Q-\alpha}$ are to be identified. For $\alpha=\frac{Q}{2}+i P, P\in \mathbb{R}$
fields $V_{\alpha}$ are non-local.

Computation of correlation functions in Liouville field theory relies on screening operators and
recurrent relations that appear from OPE for auxiliary correlation functions.
\subsection{Coulomb gas representation and screening operators}
\label{sec:coul-gas-repr}

\subsection{Boundary Liouville theory}
\label{sec:bound-liouv-theory}

@@

In paper \cite{fateev2000boundary} following expression was obtained for one-point boundary
correlation function
\begin{equation}
  \label{eq:22}
  \left<V_{\alpha}(x)\right>=\frac{U(\alpha|\mu_{B})}{|z-\bar z|^{2\Delta_{\alpha}}}
\end{equation}

\begin{equation}
  \label{eq:21}
  U(\alpha)=\frac{2}{b}\left(\pi\mu\gamma( b^{2})\right)^{\frac{Q-2\alpha}{2b}} \Gamma(2b\alpha-b^{2})
  \Gamma\left(\frac{2\alpha}{b}-\frac{1}{b^{2}}-1\right) \cosh (2\alpha-Q)\pi s
\end{equation}
where $s$ is determined from the equation
\begin{equation}
  \label{eq:23}
  \cosh^{2} \pi b s=\frac{\mu_{B}^{2}}{\mu}\sin \pi b^{2}
\end{equation}
and $\gamma(x)=\frac{\Gamma(x)}{\Gamma(1-x)}$.

This one point function is related to generating function of surfaces with a conic singularity of given length and area in
two-dimensional gravity theory. 
Partition function for  surfaces with a conic singularity of given length and area in
two-dimensional gravity theory is denoted by $Z_{\alpha}(A,l)$. Canonical transformation gives us
\begin{equation}
  \label{eq:24}
  W_{\alpha}(l,\mu)=\int_{0}^{\infty} \frac{dA}{A} e^{-\mu A}Z_{\alpha}(A,l)
\end{equation}

Note that number of surfaces of given area $A$ and length $l$ is given by a canonical ensemble
(parameters $N$, $E$)
\begin{equation}
  \label{eq:25}
  N(l,A) = \sum_{\mbox{surfaces}} \delta(\mbox{Area}-A)\delta(\mbox{Length}-l)
\end{equation}
\begin{equation}
  \label{eq:26}
  F=\log Z
\end{equation}
Using Legendre transformation ($f^{*}(p)=\sup_{x\in I} (xp - f(x))$ $x\to \mbox{tangent}$) we move
to the description with bulk and boundary interaction constants. 
\begin{equation}
  \label{eq:27}
  \min_{\mu}(F(\mu)-\mu A) = S = \log N(A) \quad \mbox{Enthropy}
\end{equation}
Thus we obtain grand canonical ensemble (number of particles is not fixed, $w_{n}=\frac{1}{Z}
e^{\frac{-(E_{n}-\mu N)}{kT}}$)

$Z(\mu_{B},\mu) = \sum_{\mbox{surfaces}} e^{-\mu_{B}l -\mu A}=\int D\varphi e^{-S[\varphi]}$
\begin{equation}
  \label{eq:28}
  \int D\varphi = \int dA dl \int D\phi \quad \mbox{but} \quad \int D\phi = N(A,l)
\end{equation}
It is useful to note different definition of integration measure in \cite{fateev2000boundary}: $\int
\frac{d A}{A}\frac{d l }{l} N(A,l)$
\section{Scaling limit and CFT on a cone}
\label{sec:scaling-limit-cft}
